Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-18 ICML-submission/introduction.tex
elaboration on Chen et al

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their proof of
Theorem 2 is incorrect: their Lemma 4 cannot be directly applied to the bandit
setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We
design a simple and efficient algorithm
(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
that makes at most $O(K (R/\gamma)^2))$ mistakes in expectation. Its memory
complexity and per-round time complexity are both $O(dK)$. The algorithm can be
viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
copy for each class. We prove that any (possibly randomized) algorithm must make
$\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
multiplicative factor the mistake bound, as compared to the full-information
setting, is the price we pay for the bandit feedback, or more precisely, the
lack of full-information feedback.

>>>>

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their proof of
Theorem 2 is incorrect: first, their Theorem 2
implies a mistake upper bound of $\frac{R}{\gamma}$ with
sufficiently large $C$, which contradicts our lower
bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
second, their Lemma 4 cannot be directly applied to the bandit
setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We
design a simple and efficient algorithm
(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
that makes at most $O(K (R/\gamma)^2))$ mistakes in expectation. Its memory
complexity and per-round time complexity are both $O(dK)$. The algorithm can be
viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
copy for each class. We prove that any (possibly randomized) algorithm must make
$\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
multiplicative factor the mistake bound, as compared to the full-information
setting, is the price we pay for the bandit feedback, or more precisely, the
lack of full-information feedback.
